Open-source landscape for 3D CSEM modelling

### 2020-06-28 manuscript/Manuscript.tex
fix Haber book reference

The electromagnetics implementations use a staggered grid finite volume
approach where physical properties are discretized at cell centers, fields on
cell edges and fluxes on cell faces \citep{IEEE.66.Yee} (for an overview of
discretizing Maxwell's equations, we recommend \cite{Haber2014}). There are
two different discretization strategies implemented for Maxwell's equations: (
a) the EB-formulation, which discretizes the electric field ($\vec{e}$) on
cell edges and the magnetic flux density ($\vec{h}$) on cell faces, and (b)
the HJ-formulation, which discretizes the magnetic field ($\vec{h}$) on cell
edges and the current density ($\vec{j}$) on cell faces. In both cases the
physical properties: electrical conductivity / resistivity and magnetic
permeability are discretized at cell centers. Having multiple implementations
allows for testing that compares results from each approach, as well as the
representation of both electrical and magnetic sources on cylindrically
symmetric meshes. \simpeg supports variable magnetic permeability and
full-tensor anisotropy for the physical properties.

>>>>

The electromagnetics implementations use a staggered grid finite volume
approach where physical properties are discretized at cell centers, fields on
cell edges and fluxes on cell faces \citep{IEEE.66.Yee} (for an overview of
discretizing Maxwell's equations, we recommend \cite{Haber2014b}). There are
two different discretization strategies implemented for Maxwell's equations: (
a) the EB-formulation, which discretizes the electric field ($\vec{e}$) on
cell edges and the magnetic flux density ($\vec{h}$) on cell faces, and (b)
the HJ-formulation, which discretizes the magnetic field ($\vec{h}$) on cell
edges and the current density ($\vec{j}$) on cell faces. In both cases the
physical properties: electrical conductivity / resistivity and magnetic
permeability are discretized at cell centers. Having multiple implementations
allows for testing that compares results from each approach, as well as the
representation of both electrical and magnetic sources on cylindrically
symmetric meshes. \simpeg supports variable magnetic permeability and
full-tensor anisotropy for the physical properties.
